Short Paper \\\large{A Short Subtitle}

### 2024-01-03 apples_and_oranges.tex
Having problems with my git, hoping this will fix merge errors

\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\makeatother
\journal{Journal Name}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[]{natbib}
\bibliographystyle{elsarticle-num}
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Short Paper},
  pdfauthor={Alice Anonymous; Bob Security; Cat Memes; Derek Zoolander},
  pdfkeywords={keyword1, keyword2},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\begin{frontmatter}
\title{Short Paper \\\large{A Short Subtitle} }
\author[1]{Alice Anonymous%
\corref{cor1}%
\fnref{fn1}}
 \ead{alice@example.com} 
\author[2]{Bob Security%
%
\fnref{fn2}}
 \ead{bob@example.com} 
\author[2]{Cat Memes%
%
\fnref{fn3}}
 \ead{cat@example.com} 
\author[]{Derek Zoolander%
%
}
 \ead{derek@example.com}

\affiliation[1]{organization={Some Institute of Technology, Department
Name},addressline={Street Address},city={City},postcode={Postal
Code},postcodesep={}}
\affiliation[2]{organization={Another University, Department
Name},addressline={Street Address},city={City},postcode={Postal
Code},postcodesep={}}

\cortext[cor1]{Corresponding author}
\fntext[fn1]{This is the first author footnote.}
\fntext[fn2]{Another author footnote, this is a very long footnote and
it should be a really long footnote. But this footnote is not yet
sufficiently long enough to make two lines of footnote text.}
\fntext[fn3]{Yet another author footnote.}

\begin{abstract}
This is the abstract. Lorem ipsum dolor sit amet, consectetur adipiscing
elit. Vestibulum augue turpis, dictum non malesuada a, volutpat eget
velit. Nam placerat turpis purus, eu tristique ex tincidunt et. Mauris
sed augue eget turpis ultrices tincidunt. Sed et mi in leo porta
egestas. Aliquam non laoreet velit. Nunc quis ex vitae eros aliquet
auctor nec ac libero. Duis laoreet sapien eu mi luctus, in bibendum leo
molestie. Sed hendrerit diam diam, ac dapibus nisl volutpat vitae.
Aliquam bibendum varius libero, eu efficitur justo rutrum at. Sed at
tempus elit.
\end{abstract}

\begin{keyword}
    keyword1 \sep 
    keyword2
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}, frame hidden, breakable, enhanced, sharp corners]}{\end{tcolorbox}}\fi

Please make sure that your manuscript follows the guidelines in the
Guide for Authors of the relevant journal. It is not necessary to
typeset your manuscript in exactly the same way as an article, unless
you are submitting to a camera-ready copy (CRC) journal.

For detailed instructions regarding the elsevier article class, see
\url{https://www.elsevier.com/authors/policies-and-guidelines/latex-instructions}

\hypertarget{bibliography-styles}{%
\section{Bibliography styles}\label{bibliography-styles}}

Here are two sample references: \citet{Feynman1963118}
\citet{Dirac1953888}.

By default, natbib will be used with the \texttt{authoryear} style, set
in \texttt{classoption} variable in YAML. You can sets extra options
with \texttt{natbiboptions} variable in YAML header. Example

\begin{verbatim}
natbiboptions: longnamesfirst,angle,semicolon
\end{verbatim}

There are various more specific bibliography styles available at
\url{https://support.stmdocs.in/wiki/index.php?title=Model-wise_bibliographic_style_files}.
To use one of these, add it in the header using, for example,
\texttt{biblio-style:\ model1-num-names}.

\hypertarget{using-csl}{%
\subsection{Using CSL}\label{using-csl}}

If \texttt{cite-method} is set to \texttt{citeproc} in
\texttt{elsevier\_article()}, then pandoc is used for citations instead
of \texttt{natbib}. In this case, the \texttt{csl} option is used to
format the references. By default, this template will provide an
appropriate style, but alternative \texttt{csl} files are available from
\url{https://www.zotero.org/styles?q=elsevier}. These can be downloaded
and stored locally, or the url can be used as in the example header.

\hypertarget{equations}{%
\section{Equations}\label{equations}}

Here is an equation: \[ 
  f_{X}(x) = \left(\frac{\alpha}{\beta}\right)
  \left(\frac{x}{\beta}\right)^{\alpha-1}
  e^{-\left(\frac{x}{\beta}\right)^{\alpha}}; 
  \alpha,\beta,x > 0 .
\]

Inline equations work as well: \(\sum_{i = 2}^\infty\{\alpha_i^\beta\}\)

@@

Figure~\ref{fig-meaningless} is generated using an R chunk.

@@

{\centering \includegraphics[width=0.5\textwidth,height=\textheight]{elsevier_files/figure-pdf/fig-meaningless-1.pdf}

}

\caption{\label{fig-meaningless}A meaningless scatterplot}

@@

\hypertarget{tables-coming-from-r}{%
\section{Tables coming from R}\label{tables-coming-from-r}}

Tables can also be generated using R chunks, as shown in
Table~\ref{tbl-simple} example.

@@

\renewcommand\refname{References}
  \bibliography{bibliography.bib}

>>>>

\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\makeatother
\journal{Journal Name}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[]{natbib}
\bibliographystyle{elsarticle-num}
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Fundamental Problems with the Evidence Base for Adolescent Depression Treatments.},
  pdfauthor={Argyris Stringaris; Charlotte Burman; Dayna Bhudia; Carmen Moreno; Samuele Cortese; Georgina Krebs},
  pdfkeywords={depression, adolescents, antidepressants, psychotherapy},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\begin{frontmatter}
\title{Fundamental Problems with the Evidence Base for Adolescent
Depression Treatments. \\\large{A conceptual and quantiative
re-appraisal.} }
\author[1]{Argyris Stringaris%
\corref{cor1}%
}
 \ead{a.stringaris@ucl.ac.uk} 
\author[1]{Charlotte Burman%
%
}
 \ead{c.burman@ucl.ac.uk} 
\author[1]{Dayna Bhudia%
%
}
 \ead{d.bhudia@ucl.ac.uk} 
\author[2]{Carmen Moreno%
%
}
 \ead{cmoreno@hggm.es} 
\author[3]{Samuele Cortese%
%
}
 \ead{samuele.cortese@soton.ac.uk} 
\author[1]{Georgina Krebs%
%
}
 \ead{g.krebs@ucl.ac.uk}

\affiliation[1]{organization={University College London, Divisions of
Psychiatry and Psychology and Language Science},addressline={1-19
Torrington Place},city={London, UK},country={United
Kingdom},countrysep={,},postcode={WC1E 7HB},postcodesep={}}
\affiliation[2]{organization={Hospital Gregorio Marañón, Department of
Psychiatry},addressline={46 C. del
Dr.~Esquerdo},city={Madrid},country={Spain},countrysep={,},postcode={28007},postcodesep={}}
\affiliation[3]{organization={University of Southampton, Centre for
Innovation in Mental Health (CIMH), School of
Psychology},addressline={Highfield Campus, Building
44},city={Southampton},country={United
Kingdom},countrysep={,},postcode={SO17 1BJ},postcodesep={}}

\cortext[cor1]{Corresponding author}

\begin{abstract}
To follow
\end{abstract}

\begin{keyword}
    depression \sep adolescents \sep antidepressants \sep 
    psychotherapy
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[sharp corners, boxrule=0pt, interior hidden, frame hidden, borderline west={3pt}{0pt}{shadecolor}, breakable, enhanced]}{\end{tcolorbox}}\fi

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

Depression is the leading cause of disability in adolescents and
influential guidelines recommend that it be treated with either
psychotherapy or anti-depressant medication or their combination. The
evidence base for this recommendation typically derives from the
appraisal of randomised controlled trials (RCTs) in which one modality
(psychotherapy or anti-depressants) are compared against a control
condition. In this paper we identify a series of fundamental problems
with this appraisal and make recommendations on how it can be improved.

Guidelines make implicit and explicit \ldots{} comparisons\ldots{}

Network metanalyses\ldots{}

Jureidini approach\ldots summarises.

This state of affairs is reflected in textbooks and also in what
trainees in psychiatry and psychology learn QUOTE.

Yet, is this approach correct?

This approach relies on a (explicit or more often implicit) comparison
of the two treatment modalities. Ideally, a comparison between the
treatment modalities should be direct, that is head to head. Only one
such trial exists in adolescent depression (from the TADS study, see
below) which showed that fluoxetine was superior to both cognitive and
behavioural therapy (CBT) as well as placebo, and that CBT did not
differentiate from placebo. Apart from this one study, all other
comparisons indirect, that is, they have to be inferred from comparing
studies where an antidepressant or a psychotherapy is compared to a
control condition; the control conditions for antidepressant studies is
the placebo (standard also in the rest of medicine), whilst controls for
psychotherapy studies can vary substantially from waiting list, to
treatment as usual to an attention control, such as psychoeducation.
These comparisons therefore have to rely on testing whether the
following simple equality holds or not,

\begin{equation}\protect\hypertarget{eq-1}{}{Effect_{Med} = Effect_{Psy}}\label{eq-1}\end{equation}

where \emph{Effect} denotes the effect on depression that either
medication (\emph{Med} ) or psychotherapy (\emph{Psy}) have. This
comparison is achieved by comparing some measure of effect,
e.g.~percentage response or standardised mean difference, for each
medication and psychotherapy. The simplest way of doing such a
comparison is to take pooled estimates of such effects from metanalyses
of each anti-depressants and psychotherapy and compare them informally.
A more formal way of doing this is through a network metanalysis, which
uses any direct comparisons to infer indirect ones.

Yet for the indirect comparison to be valid, several assumptions need to
hold. The most important of these assumptions can be summarised using
the technical term \emph{ceteris paribus}, meaning that the results of
this comparison are valid if all else is equal. Two important such
assumptions are: a) that the control conditions for each antidepressant
and psychotherapy trials are equal---we call this the \emph{equality of
controls} assumption. b) that the effects of each treatment modality
have been derived from the same underlying population, that is that the
people who have received the treatment are similar on important
parameters on average--this we call the \emph{one population}
assumption.

Starting with the \emph{equality of controls}, its importance can be
easily intuited by expanding equation 1 to include the comparisons on
which each side of that equation rests:

\begin{equation}\protect\hypertarget{eq-2}{}{Effect_{MedActive} - Effect_{MedControls} = Effect_{PsyActive} - Effect_{PsyControls}}\label{eq-2}\end{equation}

where MedActive and PsyActive are the active arms of antidepressant and
psychotherapy trials, respectively, and MedControls and PsyControls the
respective control arms. The assumption here has to be that the controls
are equal, that is, \[ Effect_{MedControls} = Effect_{PsyControls}\]. A
few simple examples help illustrate why this assumption is important Let
the two modalities of treatment be medication and surgery, and let there
be a trial for each modality. In the medication trial 80\% of
participants respond to the antihypertensive and only 40\% to placebo;
in the surgery trial, 40\% of people respond to surgery and 0\% to sham.
If one relied on Equation 1 to compare the treatments they would arrive
at the absurd conclusion that the two treatments are equal and recommend
to a patient that it does not really matter which one they choose.
Playing around with numbers in which no equality of the respective
control arms is required, leads to other risible conclusions.

Yet, surprisingly, a focus on the equality of controls is largely absent
from appraisals of the evidence of medication and psychotherapy.

Moving on to the \emph{one population} assumption, this can be
formalised

\citet{stringarisDevelopmentalPathwaysChildhood2014}

@@

@@

\includegraphics[width=12.5in,height=\textheight]{forestplot.png} \hfill{}

\caption{Forest Plot of Control Arms by the Control Arm of Each
Treatment Modality.}

@@

\begin{verbatim}
\end{verbatim}

\hypertarget{tables-coming-from-rtable}{%
\section{Tables coming from RTable}\label{tables-coming-from-rtable}}

@@

  \bibliography{emotion\_concepts\_paper.bib}

### 2024-01-03 elsevier/elsevier.tex
Having problems with my git, hoping this will fix merge errors

\begin{keyword}
    keyword1 \sep 
    keyword2
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}, frame hidden, breakable, enhanced, sharp corners]}{\end{tcolorbox}}\fi

>>>>

\begin{keyword}
    keyword1 \sep 
    keyword2
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, borderline west={3pt}{0pt}{shadecolor}, boxrule=0pt, breakable, frame hidden, enhanced, sharp corners]}{\end{tcolorbox}}\fi
